Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2019-02-13 paper/ms.tex
put in Carlyn's cleaned figs and add plotscripts

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_hybrid.png}
\caption{\label{fig:nithybrid}
Estimated \Ni{56} mass vs.\ time for ten hybrid model explosion simulations. 
Shown are realizations 21-30. 
}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_vs_time_CO.png}
\caption{\label{fig:nitco}
Estimated \Ni{56} mass vs.\ time for ten C-O model explosion simulations.
Shown are realizations 21-30. 
}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_ratio_v2.png}
\caption{\label{fig:compare_ratio}
Plot of estimated \Ni{56} mass vs.\ time showing the evolution
for both suites of simulations. Results from 
C-O-Ne progenitors are in red and C-O progenitors blue. 
{\color{red} SAME AS DON'S FIGURE 19}.
%SAME AS DON'S FIGURE 19
}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_burned_mass_v2.png}
\caption{\label{fig:compare_burned}
Plot of estimated mass burned to IGEs vs.\ time showing the evolution
for both suites of simulations. Results from C-O-Ne progenitors are 
in red and C-O progenitors blue.  
Note that one of the C/O simulations presented did not complete.
%SAME AS DON'S FIGURE 20
{\color{red} SAME AS DON'S FIGURE 20.} 
}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{figures/Hybrid_Ni56mass_v_time_plot.pdf}
\caption{\label{fig:nithybrid}
Estimated \Ni{56} mass vs.\ time for ten hybrid model explosion simulations. 
Shown are realizations 21-30. 
}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/CO_Ni56mass_v_time_plot.pdf}
\caption{\label{fig:nitco}
Estimated \Ni{56} mass vs.\ time for ten C-O model explosion simulations.
Shown are realizations 21-30. 
}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/RatioNi56IGE_v_time_plot.pdf}
\caption{\label{fig:compare_ratio}
Plot of estimated \Ni{56} mass vs.\ time showing the evolution
for both suites of simulations. Results from 
C-O-Ne progenitors are in red and C-O progenitors blue. 
{\color{red} SAME AS DON'S FIGURE 19}.
%SAME AS DON'S FIGURE 19
}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/MBTI_v_time_plot.pdf}
\caption{\label{fig:compare_burned}
Plot of estimated mass burned to IGEs vs.\ time showing the evolution
for both suites of simulations. Results from C-O-Ne progenitors are 
in red and C-O progenitors blue.  
Note that one of the C/O simulations presented did not complete.
%SAME AS DON'S FIGURE 20
{\color{red} SAME AS DON'S FIGURE 20.} 
}
\end{figure}
